---
title: "S4"
output: 
  html_document:
    toc: true
    toc_float:
      smooth_scroll: FALSE
    number_sections: true
---

This appendix illustrates the process of fitting various parameterisations
of the $SE^1I^jR$ model ($M^{1j}$ & $M^{3j}$) to **Poisson $D^{3j}$** 
incidence reports. We mean by *parameterisation* the decision of categorising 
parameters as either *unknown* or *assumed*. For unknown parameters, we 
construct prior distributions, which will be eventually updated in light of the
data via HMC sampling, resulting in a posterior distribution. On the other hand,
assumed parameters are fixed at their true values.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(cmdstanr)
library(dplyr)
library(Metrics)
library(purrr)
library(readr)
library(readsdr)
library(rstan)
library(stringr)
library(tictoc)
library(tidyr)

source("./R_scripts/Inference.R")
source("./R_scripts/formulas.R")
source("./R_scripts/model_selection.R")
source("./R_scripts/plots.R")
source("./R_scripts/posterior_utils.R")
source("./R_scripts/SEIR_stan_files.R")
source("./R_scripts/synthetic_data.R")
source("./R_scripts/tables.R")
source("./R_scripts/utils.R")
```

```{r}
params_df <- read_csv("./data/param_values.csv", show_col_types = FALSE)

# Latent period
inv_sigma_val <- params_df |> filter(name == "inv_sigma") |> pull(value)
# Infectious period
inv_gamma_val <- params_df |> filter(name == "inv_gamma") |> pull(value)
# Effective contact rate
beta_val      <- params_df |> filter(name == "beta") |> pull(value)
# Reporting rate
rho_val       <- params_df |> filter(name == "rho") |> pull(value)

R0_val        <- beta_val * inv_gamma_val

y_df          <- read_csv("./data/Synthetic/SEIR/Case_3.csv")
```

```{r}
n_chains          <- 4
samples_per_chain <- 1000
M_j       <- 1:4
```

# Three-unknown

As the name suggests, for candidates from this parameterisation, we assume that
two parameters and one initial condition are unknown: $\beta$, $\rho$, and 
$I^1_0$. Each candidate is coupled with the Poisson distribution. 

## Prior distributions {#link1}

The prior distributions shown below apply for all candidates from this 
parameterisation.

### Effective contact rate ($\beta$)

```{r, fig.align='left', fig.height = 3, fig.width = 5}
prior_df <- data.frame(x = rlnorm(1e5))

plot_prior(prior_df, "beta", "beta~'~ lognormal(0,1)'", c(0, 10), 25)
```

### Reporting rate ($\rho$)

```{r, fig.align='left', fig.height = 3, fig.width = 5}
prior_df <- data.frame(x = rbeta(1e5, 2, 2))

plot_prior(prior_df, "rho", "rho~'~ beta(2, 2)'", c(0, 1), 15)
```

### Initial number of infectious individuals ($I_0$)

```{r, fig.align='left', fig.height = 3, fig.width = 5}
prior_df <- data.frame(x = rlnorm(1e5))

plot_prior(prior_df, "I[0]", "I[0]~'~ lognormal(0,1)'", c(0, 10), 25)
```


## Posterior distributions

We stratify inference results by the distribution of the infectious period that
produced the observed incidences. For instance, $D_{31}$ implies that the fitted
incidence stems from an SEIR with an gamma-distributed latent (shape = 3) period
and an exponential-distributed infectious period.

```{r}
root_fldr <- "./Saved_objects/Inference/Synthetic_data/SEIR/Case_3/Three_params"

all_files <- readRDS("./Stan_files/Inference/Three_params/pois/meta_info.rds")
n_params  <- 5

ll_list_right  <- vector(mode = "list", length = length(M_j))
ll_list_wrong  <- vector(mode = "list", length = length(M_j))
```

### Fitting $D^{31}$

```{r}
D_i    <- 3
D_j    <- 1
n_data <- 20
```

```{r}
M_i        <- 3
fltr       <- map_lgl(all_files, \(fl_list) fl_list$E_ord == M_i)
info_files <- all_files[fltr]

create_backup_fldrs(D_i, D_j, n_data, M_i, M_j, root_fldr)
```

```{r}
ll_list_right[[D_j]] <- fit_datasets(D_i, D_j, n_data, y_df, info_files, 
                               root_fldr, n_chains, samples_per_chain,
                               n_params = n_params)
```

```{r, wrong_E_1}
M_i        <- 1
fltr       <- map_lgl(all_files, \(fl_list) fl_list$E_ord == M_i)
info_files <- all_files[fltr]

create_backup_fldrs(D_i, D_j, n_data, M_i, M_j, root_fldr)
```

```{r}
ll_list_wrong[[D_j]] <- fit_datasets(D_i, D_j, n_data, y_df, info_files, 
                               root_fldr, n_chains, samples_per_chain, 
                               n_params = n_params)
```

```{r}
ds               <- 4
posterior_sample <- bind_rows(ll_list_right[[D_j]][[ds]],
                              ll_list_wrong[[D_j]][[ds]])
        
ds_subset          <- c(4, 8, 12, 16)

posterior_subset <- lapply(ds_subset, \(ds) {
  bind_rows(ll_list_right[[D_j]][[ds]],
            ll_list_wrong[[D_j]][[ds]])
})
```

#### Incidence fit

The figure below compares actual (points) and simulated (lines) latent incidence
by model candidate.

```{r}
set.seed(1509)
incidence_df <- extract_incidence(posterior_sample, 40)
plot_incidence_prediction(incidence_df, y_df, D_i, D_j, ds)
```

We draw on the mean absolute scaled error (MASE) to compare incidence fits. This
quantity is a measure of the accuracy of forecasts, well-suited for time-series.
Therefore, we employ the MASE to compare each of the 4000 simulated latent 
incidences against its true counterpart ($x$) and observed incidence ($y$). By 
simulated latent incidences, we refer to the process of plugging a posterior 
distribution (samples) into an ODE model to obtain incidence trajectories via
simulation. We summarise the results via histograms in the plot below. The left
column (of panels) contains the comparison between simulated and actual latent 
incidences. The right column of panels displays the comparison between simulated
latent incidence and the observed incidence. Overall, there is no noticeable
difference in the histograms as the distribution of the infectious period in the
fitting model varies (increasing $j$). In stark contrast, assuming the wrong
distribution of the latent period leads to suboptimal incidence fits. Notice
that assuming a gamma-distributed latent period with shape 3 ($i = 3$) produces
better fits (lower MASE) than a model with the same distribution of the 
infectious period, but with an exponentially-distributed latent period ($i = 1$).

```{r}
plot_hist_mase2(posterior_sample, y_df, c(0, 0.75))
```

#### Joint posterior distribution (right $i$)

In this plot, we show an example of a joint posterior distribution. 
Specifically, this posterior distribution was derived from fitting the $M^{31}$
candidate to one $D^{31}$ incidence report.

```{r}
joint_posterior_df <- posterior_sample |> filter(M_i == !!D_i,
                                                 M_j == !!D_j) |> 
  select(par_beta, par_rho, I0)

pairs_posterior(joint_posterior_df, strip_text = 10, axis_text_size = 7,
                M_j = D_j)
```

#### Joint posterior distribution (wrong $i$)

This posterior distribution was obtained from fitting the $M^{11}$ candidate to
one $D^{31}$ incidence report.

```{r}
joint_posterior_df <- posterior_sample |> filter(M_i != !!D_i,
                                                 M_j == !!D_j) |> 
  select(par_beta, par_rho, I0)

pairs_posterior(joint_posterior_df, strip_text = 10, axis_text_size = 7,
                M_j = D_j)
```

#### Marginal posterior distributions

In this section, we present a comparison between estimated marginal posterior 
distributions (error bars) and actual values (vertical lines). Such 
distributions are the result of fitting  all eight candidates to four $D^{31}$ 
incidence reports. The value in the middle of the error bars indicates the
relative error between the actual value and the mean of the marginal posterior
distribution.

##### Basic reproduction number ($\Re_0$)

```{r}
plot_R0_comparison_by_dataset(posterior_subset, R0_val, 2.1, 2.6, D_i, D_j)
```

##### Reporting rate ($\rho$) 

```{r}
plot_par_estimates_by_dataset(posterior_subset, "par_rho", rho_val, 
                              x_min = 0.5, x_max = 1, x_label = "rho",
                              D_i, D_j)
```

##### Initial number of infectious individuals ($I_0$)

```{r}
plot_par_estimates_by_dataset(posterior_subset, "I0", 1, x_min = 0,
                              x_max = 1.5, x_label = "I[0]", D_i, D_j)
```

### Fitting $D^{32}$

```{r}
D_i    <- 3
D_j    <- 2
n_data <- 20
```

```{r}
M_i        <- 3
fltr       <- map_lgl(all_files, \(fl_list) fl_list$E_ord == M_i)
info_files <- all_files[fltr]

create_backup_fldrs(D_i, D_j, n_data, M_i, M_j, root_fldr)
```

```{r}
ll_list_right[[D_j]] <- fit_datasets(D_i, D_j, n_data, y_df, info_files, 
                               root_fldr, n_chains, samples_per_chain,
                               n_params = n_params)
```

```{r}
M_i        <- 1
fltr       <- map_lgl(all_files, \(fl_list) fl_list$E_ord == M_i)
info_files <- all_files[fltr]

create_backup_fldrs(D_i, D_j, n_data, M_i, M_j, root_fldr)
```

```{r}
ll_list_wrong[[D_j]] <- fit_datasets(D_i, D_j, n_data, y_df, info_files, 
                               root_fldr, n_chains, samples_per_chain,
                               n_params = n_params)
```

```{r}
ds               <- 4
posterior_sample <- bind_rows(ll_list_right[[D_j]][[ds]],
                              ll_list_wrong[[D_j]][[ds]])
        
ds_subset          <- c(4, 8, 12, 16)

posterior_subset <- lapply(ds_subset, \(ds) {
  bind_rows(ll_list_right[[D_j]][[ds]],
            ll_list_wrong[[D_j]][[ds]])
})
```

#### Incidence fit

```{r}
set.seed(1117)
incidence_df <- extract_incidence(posterior_sample, 40)
plot_incidence_prediction(incidence_df, y_df, D_i, D_j, ds)
```

```{r}
plot_hist_mase2(posterior_sample, y_df, c(0, 0.75))
```

#### Joint posterior distribution (right $i$)

This posterior distribution was derived from fitting the $M^{32}$
candidate to one $D^{32}$ incidence report.

```{r}
joint_posterior_df <- posterior_sample |> filter(M_i == !!D_i,
                                                 M_j == !!D_j) |> 
  select(par_beta, par_rho, I0)

pairs_posterior(joint_posterior_df, strip_text = 10, axis_text_size = 7,
                M_j = D_j)
```

#### Joint posterior distribution (wrong $i$)

This posterior distribution was obtained from fitting the $M^{12}$ candidate to
one $D^{32}$ incidence report.

```{r}
joint_posterior_df <- posterior_sample |> filter(M_i != !!D_i,
                                                 M_j == !!D_j) |> 
  select(par_beta, par_rho, I0)

pairs_posterior(joint_posterior_df, strip_text = 10, axis_text_size = 7,
                M_j = D_j)
```

#### Marginal posterior distributions

##### Basic reproduction number ($\Re_0$)

```{r}
plot_R0_comparison_by_dataset(posterior_subset, R0_val, 2, 3, D_i, D_j)
```

##### Reporting rate ($\rho$) 

```{r}
plot_par_estimates_by_dataset(posterior_subset, "par_rho", rho_val, 
                              x_min = 0.5, x_max = 1, x_label = "rho",
                              D_i, D_j)
```

##### Initial number of infectious individuals ($I_0$)

```{r}
plot_par_estimates_by_dataset(posterior_subset, "I0", 1, x_min = 0,
                              x_max = 1.5, x_label = "I[0]", D_i, D_j)
```

### Fitting $D^{33}$

```{r}
D_i    <- 3
D_j    <- 3
n_data <- 20
```

```{r}
M_i        <- 3
fltr       <- map_lgl(all_files, \(fl_list) fl_list$E_ord == M_i)
info_files <- all_files[fltr]

create_backup_fldrs(D_i, D_j, n_data, M_i, M_j, root_fldr)
```

```{r}
ll_list_right[[D_j]] <- fit_datasets(D_i, D_j, n_data, y_df, info_files, 
                               root_fldr, n_chains, samples_per_chain, 
                               n_params = n_params)
```

```{r}
M_i        <- 1
fltr       <- map_lgl(all_files, \(fl_list) fl_list$E_ord == M_i)
info_files <- all_files[fltr]

create_backup_fldrs(D_i, D_j, n_data, M_i, M_j, root_fldr)
```

```{r}
ll_list_wrong[[D_j]] <- fit_datasets(D_i, D_j, n_data, y_df, info_files, 
                               root_fldr, n_chains, samples_per_chain,
                               n_params = n_params)
```

```{r}
ds               <- 4
posterior_sample <- bind_rows(ll_list_right[[D_j]][[ds]],
                              ll_list_wrong[[D_j]][[ds]])
        
ds_subset          <- c(4, 8, 12, 16)

posterior_subset <- lapply(ds_subset, \(ds) {
  bind_rows(ll_list_right[[D_j]][[ds]],
            ll_list_wrong[[D_j]][[ds]])
})
```

#### Incidence fit

```{r}
set.seed(1129)
incidence_df <- extract_incidence(posterior_sample, 40)
plot_incidence_prediction(incidence_df, y_df, D_i, D_j, ds)
```

```{r}
plot_hist_mase2(posterior_sample, y_df, c(0, 0.75))
```

#### Joint posterior distribution (right $i$)

This posterior distribution was derived from fitting the $M^{33}$
candidate to one $D^{33}$ incidence report.

```{r}
joint_posterior_df <- posterior_sample |> filter(M_i == !!D_i,
                                                 M_j == !!D_j) |> 
  select(par_beta, par_rho, I0)

pairs_posterior(joint_posterior_df, strip_text = 10, axis_text_size = 7,
                M_j = D_j)
```

#### Joint posterior distribution (wrong $i$)

This posterior distribution was obtained from fitting the $M^{13}$ candidate to
one $D^{33}$ incidence report.

```{r}
joint_posterior_df <- posterior_sample |> filter(M_i != !!D_i,
                                                 M_j == !!D_j) |> 
  select(par_beta, par_rho, I0)

pairs_posterior(joint_posterior_df, strip_text = 10, axis_text_size = 7,
                M_j = D_j)
```

#### Marginal posterior distributions

##### Basic reproduction number ($\Re_0$)

```{r}
plot_R0_comparison_by_dataset(posterior_subset, R0_val, 2, 3, D_i, D_j)
```

##### Reporting rate ($\rho$) 

```{r}
plot_par_estimates_by_dataset(posterior_subset, "par_rho", rho_val, 
                              x_min = 0.5, x_max = 1, x_label = "rho",
                              D_i, D_j)
```

##### Initial number of infectious individuals ($I_0$)

```{r}
plot_par_estimates_by_dataset(posterior_subset, "I0", 1, x_min = 0,
                              x_max = 1.5, x_label = "I[0]", D_i, D_j)
```

### Fitting $D^{34}$

```{r}
D_i    <- 3
D_j    <- 4
n_data <- 20
```

```{r}
M_i        <- 3
fltr       <- map_lgl(all_files, \(fl_list) fl_list$E_ord == M_i)
info_files <- all_files[fltr]

create_backup_fldrs(D_i, D_j, n_data, M_i, M_j, root_fldr)
```

```{r}
ll_list_right[[D_j]] <- fit_datasets(D_i, D_j, n_data, y_df, info_files, 
                               root_fldr, n_chains, samples_per_chain,
                               n_params = n_params)
```

```{r}
M_i        <- 1
fltr       <- map_lgl(all_files, \(fl_list) fl_list$E_ord == M_i)
info_files <- all_files[fltr]

create_backup_fldrs(D_i, D_j, n_data, M_i, M_j, root_fldr)
```

```{r}
ll_list_wrong[[D_j]] <- fit_datasets(D_i, D_j, n_data, y_df, info_files, 
                               root_fldr, n_chains, samples_per_chain,
                               n_params = n_params)
```

```{r}
ds               <- 4
posterior_sample <- bind_rows(ll_list_right[[D_j]][[ds]],
                              ll_list_wrong[[D_j]][[ds]])
        
ds_subset          <- c(4, 8, 12, 16)

posterior_subset <- lapply(ds_subset, \(ds) {
  bind_rows(ll_list_right[[D_j]][[ds]],
            ll_list_wrong[[D_j]][[ds]])
})
```

#### Incidence fit

```{r}
set.seed(1138)
incidence_df <- extract_incidence(posterior_sample, 20)
plot_incidence_prediction(incidence_df, y_df, D_i, D_j, ds)
```

```{r}
plot_hist_mase2(posterior_sample, y_df, c(0, 0.75))
```

#### Joint posterior distribution (right $i$)

This posterior distribution was derived from fitting the $M^{34}$
candidate to one $D^{34}$ incidence report.

```{r}
joint_posterior_df <- posterior_sample |> filter(M_i == !!D_i,
                                                 M_j == !!D_j) |> 
  select(par_beta, par_rho, I0)

pairs_posterior(joint_posterior_df, strip_text = 10, axis_text_size = 7,
                M_j = D_j)
```


#### Joint posterior distribution (wrong $j$)

This posterior distribution was obtained from fitting the $M^{14}$ candidate to
one $D^{34}$ incidence report.

```{r}
joint_posterior_df <- posterior_sample |> filter(M_i != !!D_i,
                                                 M_j == !!D_j) |> 
  select(par_beta, par_rho, I0)

pairs_posterior(joint_posterior_df, strip_text = 10, axis_text_size = 7,
                M_j = D_j)
```

#### Marginal posterior distributions

##### Basic reproduction number ($\Re_0$)

```{r}
plot_R0_comparison_by_dataset(posterior_subset, R0_val, 2, 3, D_i, D_j)
```

##### Reporting rate ($\rho$) 

```{r}
plot_par_estimates_by_dataset(posterior_subset, "par_rho", rho_val, 
                              x_min = 0.5, x_max = 1, x_label = "rho",
                              D_i, D_j)
```

##### Initial number of infectious individuals ($I_0$)

```{r}
plot_par_estimates_by_dataset(posterior_subset, "I0", 1, x_min = 0,
                              x_max = 1.5, x_label = "I[0]", D_i, D_j)
```

### Summary

#### Coverage

```{r}
actual_values <- data.frame(par = c("R0", "par_rho", "I0"), 
                            actual_val = c(R0_val, rho_val, 1))

map_df(ll_list_right, calculate_coverage, actual_values, inv_gamma_val) |> 
  pivot_wider(names_from = par, values_from = pct_right) -> coverage_1

map_df(ll_list_wrong, calculate_coverage, actual_values, inv_gamma_val) |> 
  pivot_wider(names_from = par, values_from = pct_right) -> coverage_2
```

```{r}
coverage_df <- bind_rows(coverage_1, coverage_2) |> 
  arrange(D_ij)

table_coverage(coverage_df)
```

# Four unknowns

In this parameterisation, for each candidate, we assume one additional unknown
parameter: the recovery rate ($\gamma$). Furthermore, all candidates are coupled
with the Poisson distribution. In light of the equivalency found in the previous
section, we restrict model candidates to those with an exponentially-distributed
latent period ($i = 1$).

```{r}
root_fldr  <- "./Saved_objects/Inference/Synthetic_data/SEIR/Case_3/Four_params"
M_i        <- 1
M_j        <- 1:4
n_params   <- 5

all_files  <- readRDS("./Stan_files/Inference/Four_params/pois/meta_info.rds")
fltr       <- map_lgl(all_files, \(fl_list) fl_list$E_ord == M_i)
info_files <- all_files[fltr]

ll_list    <- vector(mode = "list", length = length(M_j))
```

## Prior distributions

Prior distributions for $\beta$, $\rho$, and $I^1_0$ are identical to those 
described [here](#link1).

### Recovery rate ($\gamma$)

This prior distribution assumes that the magnitude of the mean infectious 
period ($\gamma^{-1}$) is at least one.

```{r, fig.align='left', fig.height = 3, fig.width = 5}
prior_df <- data.frame(x = rbeta(1e5, 2, 2))

plot_prior(prior_df, "gamma", "gamma~'~ beta(2, 2)'", c(0, 1), 15)
```

## Posterior distributions

### Fitting $D^{31}$

```{r}
D_i    <- 3
D_j    <- 1
n_data <- 20
create_backup_fldrs(D_i, D_j, n_data, M_i, M_j, root_fldr)
```

```{r}
ll_list[[D_j]] <- fit_datasets(D_i, D_j, n_data, y_df, info_files, 
                               root_fldr, n_chains, samples_per_chain, 
                               n_params = n_params)
```

```{r}
ds               <- 5
posterior_sample <- ll_list[[D_j]][[ds]]

ds_subset        <- c(5, 9, 13, 17)
posterior_subset <- ll_list[[D_j]][ds_subset]
```

#### Incidence fit

```{r}
incidence_df <- extract_incidence(posterior_sample, 20)
plot_incidence_prediction(incidence_df, y_df, D_i, D_j, ds)
```

```{r}
plot_hist_mase(posterior_sample, y_df)
```

#### Joint posterior distribution {#link2}

```{r}
joint_posterior_df <- posterior_sample |> filter(M_j == !!D_j) |> 
  select(par_beta, par_rho, I0, par_gamma) 

pairs_posterior(joint_posterior_df, strip_text = 10, axis_text_size = 7,
                M_j = D_j)
```

#### Marginal posterior distributions


##### Basic reproduction number ($\Re_0$)

```{r}
plot_R0_comparison_by_dataset(posterior_subset, R0_val, 0, 15, D_i, D_j)
```

##### Reporting rate ($\rho$) 

```{r}
plot_par_estimates_by_dataset(posterior_subset, "par_rho", rho_val, 
                              x_min = 0.5, x_max = 1, x_label = "rho", D_i, 
                              D_j)
```

##### Initial number of infectious individuals ($I_0$)

```{r}
plot_par_estimates_by_dataset(posterior_subset, "I0", 1, x_min = 0,
                              x_max = 3, x_label = "I[0]", D_i, D_j)
```

##### Recovery rate ($\gamma$)

For this parameter, we opt for a different visualisation. Specifically, for 
each model candidate fitting a particular $D^{31}$ incidence report, we 
compare the the marginal posterior distribution against the prior
distribution via histograms. 

```{r}
prior_df <- data.frame(sims = rbeta(4e3, 2, 2))
prior_posterior_comparison(posterior_sample, prior_df, "par_gamma")
```

### Fitting $D^{32}$

```{r}
D_i    <- 3
D_j    <- 2
n_data <- 20
create_backup_fldrs(D_i, D_j, n_data, M_i, M_j, root_fldr)
```

```{r}
ll_list[[D_j]] <- fit_datasets(D_i, D_j, n_data, y_df, info_files, 
                               root_fldr, n_chains, samples_per_chain, 
                               n_params = n_params)
```

```{r}
ds               <- 5
posterior_sample <- ll_list[[D_j]][[ds]]

ds_subset        <- c(5, 9, 13, 17)
posterior_subset <- ll_list[[D_j]][ds_subset]
```

#### Incidence fit

```{r}
incidence_df <- extract_incidence(posterior_sample, 20)
plot_incidence_prediction(incidence_df, y_df, D_i, D_j, ds)
```

```{r}
plot_hist_mase(posterior_sample, y_df)
```

#### Joint posterior distribution

```{r}
joint_posterior_df <- posterior_sample |> filter(M_j == !!D_j) |> 
  select(par_beta, par_rho, I0, par_gamma) 

pairs_posterior(joint_posterior_df, strip_text = 10, axis_text_size = 7,
                M_j = D_j)
```

#### Marginal posterior distributions


##### Basic reproduction number ($\Re_0$)

```{r}
plot_R0_comparison_by_dataset(posterior_subset, R0_val, 0, 30, D_i, D_j)
```

##### Reporting rate ($\rho$)

```{r}
plot_par_estimates_by_dataset(posterior_subset, "par_rho", rho_val, 
                              x_min = 0.5, x_max = 1, x_label = "rho", D_i, 
                              D_j)
```

##### Initial number of infectious individuals ($I_0$)

```{r}
plot_par_estimates_by_dataset(posterior_subset, "I0", 1, x_min = 0,
                              x_max = 3, x_label = "I[0]", D_i, D_j)
```

##### Recovery rate ($\gamma$)

```{r}
prior_df <- data.frame(sims = rbeta(4e3, 2, 2))
prior_posterior_comparison(posterior_sample, prior_df, "par_gamma")
```

### Fitting $D^{13}$

```{r}
D_i    <- 3
D_j    <- 3
n_data <- 20
create_backup_fldrs(D_i, D_j, n_data, M_i, M_j, root_fldr)
```

```{r}
ll_list[[D_j]] <- fit_datasets(D_i, D_j, n_data, y_df, info_files, 
                               root_fldr, n_chains, samples_per_chain, 
                               n_params = n_params)
```


```{r}
ds               <- 5
posterior_sample <- ll_list[[D_j]][[ds]]

ds_subset        <- c(5, 9, 13, 17)
posterior_subset <- ll_list[[D_j]][ds_subset]
```

#### Incidence fit

```{r}
incidence_df <- extract_incidence(posterior_sample, 20)
plot_incidence_prediction(incidence_df, y_df, D_i, D_j, ds)
```

```{r}
plot_hist_mase(posterior_sample, y_df)
```

#### Joint posterior distribution

```{r}
joint_posterior_df <- posterior_sample |> filter(M_j == !!D_j) |> 
  select(par_beta, par_rho, I0, par_gamma) 

pairs_posterior(joint_posterior_df, strip_text = 10, axis_text_size = 7,
                M_j = D_j)
```

#### Marginal posterior distributions

##### Basic reproduction number ($\Re_0$)

```{r}
plot_R0_comparison_by_dataset(posterior_subset, R0_val, 0, 50, D_i, D_j)
```

##### Reporting rate ($\rho$)

```{r}
plot_par_estimates_by_dataset(posterior_subset, "par_rho", rho_val, 
                              x_min = 0.5, x_max = 1, x_label = "rho", D_i, 
                              D_j)
```

##### Initial number of infectious individuals ($I_0$)

```{r}
plot_par_estimates_by_dataset(posterior_subset, "I0", 1, x_min = 0,
                              x_max = 3, x_label = "I[0]", D_i, D_j)
```

##### Recovery rate ($\gamma$)

```{r}
prior_df <- data.frame(sims = rbeta(4e3, 2, 2))
prior_posterior_comparison(posterior_sample, prior_df, "par_gamma")
```

### Fitting $D^{14}$

```{r}
D_i    <- 3
D_j    <- 4
n_data <- 20
create_backup_fldrs(D_i, D_j, n_data, M_i, M_j, root_fldr)
```

```{r}
ll_list[[D_j]] <- fit_datasets(D_i, D_j, n_data, y_df, info_files, 
                               root_fldr, n_chains, samples_per_chain, 
                               n_params = n_params)
```


```{r}
ds               <- 5
posterior_sample <- ll_list[[D_j]][[ds]]

ds_subset        <- c(5, 9, 13, 17)
posterior_subset <- ll_list[[D_j]][ds_subset]
```

#### Incidence fit

```{r}
incidence_df <- extract_incidence(posterior_sample, 20)
plot_incidence_prediction(incidence_df, y_df, D_i, D_j, ds)
```

```{r}
plot_hist_mase(posterior_sample, y_df)
```

#### Joint posterior distribution

```{r}
joint_posterior_df <- posterior_sample |> filter(M_j == !!D_j) |> 
  select(par_beta, par_rho, I0, par_gamma) 

pairs_posterior(joint_posterior_df, strip_text = 10, axis_text_size = 7,
                M_j = D_j)
```

#### Marginal posterior distributions


##### Basic reproduction number ($\Re_0$)

```{r}
plot_R0_comparison_by_dataset(posterior_subset, R0_val, 0, 30, D_i, D_j)
```

##### Reporting rate ($\rho$)

```{r}
plot_par_estimates_by_dataset(posterior_subset, "par_rho", rho_val, 
                              x_min = 0.5, x_max = 1, x_label = "rho", D_i, 
                              D_j)
```

##### Initial number of infectious individuals ($I_0$)

```{r}
plot_par_estimates_by_dataset(posterior_subset, "I0", 1, x_min = 0,
                              x_max = 3, x_label = "I[0]", D_i, D_j)
```

##### Recovery rate ($\gamma$)

```{r}
prior_df <- data.frame(sims = rbeta(4e3, 2, 2))
prior_posterior_comparison(posterior_sample, prior_df, "par_gamma")
```

## Summary

### Coverage

```{r}
actual_values <- data.frame(par = c("R0", "par_rho", "I0", "inv_gamma"), 
                            actual_val = c(R0_val, rho_val, 1, inv_gamma_val))

map_df(ll_list, calculate_coverage, actual_values, inv_gamma_val) |> 
  pivot_wider(names_from = par, values_from = pct_right) -> coverage_df
```

```{r}
table_coverage(coverage_df)
```

### $\Re_0$ vs $\tau$

```{r}
ll_df <- map_df(ll_list, function(dataset_fitlist) {
  
  map_df(dataset_fitlist, \(posterior_df) {
    posterior_df |> 
      select(par_beta, par_gamma, par_rho, log_lik, D_i, D_j, M_i, M_j, dataset) |> 
      mutate(tau    = mean_generation_time(M_j, inv_sigma_val, 1 / par_gamma),
             R0     = par_beta / par_gamma,
             id     = paste(M_j, dataset, sep = "_"))
  })
})
```

```{r, fig.height = 6}
ll_subset <- ll_df |> filter(dataset %in% c(5, 7))

plot_scatterplot_R0_vs_tau(ll_subset, c(0,15), c(0, 10))
```

# Three-unknown (Alternative)

The *alternative parameterisation* refers to the algebraic manipulation of the
$SE^iI^jR$ framework so as to obtain a set equations wherein the basic 
reproduction number ($\Re_0$) and the mean generation time ($\tau$) are 
explicit parameters of the model. In doing so, $\beta$ and $\gamma$ become
functions of other variables rather than parameters. In these parameterisation,
we assume as unknown the basic reproduction number (its inverse), the reporting
rate ($\rho$) and initial number of infectious individuals ($I^1_0$). All of the 
other parameters are fixed to their true values.

\begin{equation}
  \begin{aligned}
    \dot{S_t}   &= -\frac{\beta(\tau, \sigma, \Re_0, i, j) S_t \sum^i_{k=1} I^k_t}{N}\\
    \dot{E^1_t} &= \frac{\beta(\tau, \sigma, \Re_0, i, j) S_t \sum^i_{k=1} I^k_t}{N} - i\sigma E^1_t \\
    \dot{E^2_t} &= i\sigma E^1_t - i\sigma E^2_t \\
    \vdots \\
    \dot{E^i_t} &= i \sigma E^{i - 1}_t - i \sigma E^i_t \\
    \dot{I^1_t} &= i \sigma E^{i - j}_t - \gamma(\beta, \Re_0)I^1_t \\
    \dot{I^2_t} &= j \gamma(\beta, \Re_0) I^{1 - j}_t - \gamma(\beta, \Re_0) I^2_t  \\
    \vdots \\
    \dot{I^j_t} &= j \gamma(\beta, \Re_0) I^{j - 1}_t - j \gamma(\beta, \Re_0) I^{j}_t \\
    \dot{R_t}   &= j \gamma(\beta, \Re_0)I^j_t
  \end{aligned}
\end{equation}

\begin{equation}
  \begin{aligned}
    \beta       &= \frac{2 j (\tau - \sigma^{-1})}{\Re_0^{-1} (j + 1)}\\
    \gamma      &= \beta \Re_0^{-1}
  \end{aligned}
\end{equation}


```{r}
root_fldr  <- "./Saved_objects/Inference/Synthetic_data/SEIR/Case_3/Three_params_alt"
M_i        <- 1
M_j        <- 1:4
n_params   <- 5

all_files  <- readRDS("./Stan_files/Inference/Three_params_alt/pois/meta_info.rds")
fltr       <- map_lgl(all_files, \(fl_list) fl_list$E_ord == M_i)
info_files <- all_files[fltr]

ll_list    <- vector(mode = "list", length = length(M_j))
```

## Prior distributions {#link1}

The prior distributions shown below apply for all candidates from this 
parameterisation. Prior distributions for $\rho$, and $I^1_0$ are identical to 
those described [here](#link1).

### The inverse of the basic reproduction number ($\Re_0^{-1}$)

Since model candidates are fitting outbreak-like incidence data, it is warranted
to assume that the basic reproduction number is higher than one ($\Re_0^{-1}$).
This observation implies that the magnitude of  its inverse is below that 
threshold. Consequently, we formulate a prior that is consistent with such a 
constraint.

```{r, fig.align='left', fig.height = 3, fig.width = 5}
prior_df <- data.frame(x = rbeta(1e5, 2, 2))

plot_prior(prior_df, "\u211c^-1", "\u211c^-1~'~ beta(2, 2)'", c(0, 1), 15)
```

## Posterior distributions

### Fitting $D^{31}$

```{r}
D_i    <- 3
D_j    <- 1
n_data <- 20 
create_backup_fldrs(D_i, D_j, n_data, M_i, M_j, root_fldr)
```

```{r}
ll_list[[D_j]] <- fit_datasets(D_i, D_j, n_data, y_df, info_files, 
                               root_fldr, n_chains, samples_per_chain, 
                               n_params = n_params, alt_param = TRUE)
```

```{r}
ds               <- 5
posterior_sample <- ll_list[[D_j]][[ds]]

ds_subset        <- c(5, 9, 14, 19)
posterior_subset <- ll_list[[D_j]][ds_subset]
```

#### Incidence fit

```{r}
incidence_df <- extract_incidence(posterior_sample, 40)
plot_incidence_prediction(incidence_df, y_df, D_i, D_j, ds)
```

```{r}
plot_hist_mase(posterior_sample, y_df)
```

##### Joint posterior distribution

```{r}
joint_posterior_df <- posterior_sample |> filter(M_j == !!D_j) |> 
  select(par_inv_R0, par_rho, I0)

pairs_posterior(joint_posterior_df, strip_text = 10, axis_text_size = 7,
                M_j = D_j)
```

#### Marginal posterior distributions


##### Basic reproduction number ($\Re_0$)

```{r}
plot_R0_comparison_by_dataset(posterior_subset, R0_val, 2.3, 2.8, D_i, D_j)
```

##### Initial number of infectious individuals ($I_0$)

```{r}
plot_par_estimates_by_dataset(posterior_subset, "I0", 1, x_min = 0,
                              x_max = 3, x_label = "I[0]", D_i, D_j)
```

### Fitting $D^{32}$

```{r}
D_i    <- 3
D_j    <- 2
n_data <- 20 
create_backup_fldrs(D_i, D_j, n_data, M_i, M_j, root_fldr)
```

```{r}
ll_list[[D_j]] <- fit_datasets(D_i, D_j, n_data, y_df, info_files, 
                               root_fldr, n_chains, samples_per_chain, 
                               n_params = n_params, alt_param = TRUE)
```

```{r}
ds               <- 5
posterior_sample <- ll_list[[D_j]][[ds]]

ds_subset        <- c(5, 9, 14, 19)
posterior_subset <- ll_list[[D_j]][ds_subset]
```

#### Incidence fit

```{r}
incidence_df <- extract_incidence(posterior_sample, 40)
plot_incidence_prediction(incidence_df, y_df, D_i, D_j, ds)
```

```{r}
plot_hist_mase(posterior_sample, y_df, c(0, 0.75))
```

##### Joint posterior distribution

```{r}
joint_posterior_df <- posterior_sample |> filter(M_j == !!D_j) |> 
  select(par_inv_R0, par_rho, I0)

pairs_posterior(joint_posterior_df, strip_text = 10, axis_text_size = 7,
                M_j = D_j)
```

#### Marginal posterior distributions


##### Basic reproduction number ($\Re_0$)

```{r}
plot_R0_comparison_by_dataset(posterior_subset, R0_val, 2, 3, D_i, D_j)
```

##### Initial number of infectious individuals ($I_0$)

```{r}
plot_par_estimates_by_dataset(posterior_subset, "I0", 1, x_min = 0,
                              x_max = 3, x_label = "I[0]", D_i, D_j)
```

### Fitting $D^{33}$

```{r}
D_i    <- 3
D_j    <- 3
n_data <- 20 
create_backup_fldrs(D_i, D_j, n_data, M_i, M_j, root_fldr)
```

```{r}
ll_list[[D_j]] <- fit_datasets(D_i, D_j, n_data, y_df, info_files, 
                               root_fldr, n_chains, samples_per_chain, 
                               n_params = n_params, alt_param = TRUE)
```

```{r}
ds               <- 5
posterior_sample <- ll_list[[D_j]][[ds]]

ds_subset        <- c(5, 9, 14, 19)
posterior_subset <- ll_list[[D_j]][ds_subset]
```

#### Incidence fit

```{r}
incidence_df <- extract_incidence(posterior_sample, 40)
plot_incidence_prediction(incidence_df, y_df, D_i, D_j, ds)
```

```{r}
plot_hist_mase(posterior_sample, y_df, c(0, 0.75))
```

##### Joint posterior distribution

```{r}
joint_posterior_df <- posterior_sample |> filter(M_j == !!D_j) |> 
  select(par_inv_R0, par_rho, I0)

pairs_posterior(joint_posterior_df, strip_text = 10, axis_text_size = 7,
                M_j = D_j)
```

#### Marginal posterior distributions

##### Basic reproduction number ($\Re_0$)

```{r}
plot_R0_comparison_by_dataset(posterior_subset, R0_val, 2, 3, D_i, D_j)
```

##### Initial number of infectious individuals ($I_0$)

```{r}
plot_par_estimates_by_dataset(posterior_subset, "I0", 1, x_min = 0,
                              x_max = 3, x_label = "I[0]", D_i, D_j)
```

### Fitting $D^{34}$

```{r}
D_i    <- 3
D_j    <- 4
n_data <- 20 
create_backup_fldrs(D_i, D_j, n_data, M_i, M_j, root_fldr)
```

```{r}
ll_list[[D_j]] <- fit_datasets(D_i, D_j, n_data, y_df, info_files, 
                               root_fldr, n_chains, samples_per_chain, 
                               n_params = n_params, alt_param = TRUE)
```

```{r}
ds               <- 5
posterior_sample <- ll_list[[D_j]][[ds]]

ds_subset        <- c(5, 9, 14, 19)
posterior_subset <- ll_list[[D_j]][ds_subset]
```

#### Incidence fit

```{r}
incidence_df <- extract_incidence(posterior_sample, 40)
plot_incidence_prediction(incidence_df, y_df, D_i, D_j, ds)
```

```{r}
plot_hist_mase(posterior_sample, y_df, c(0, 0.75))
```

##### Joint posterior distribution

```{r}
joint_posterior_df <- posterior_sample |> filter(M_j == !!D_j) |> 
  select(par_inv_R0, par_rho, I0)

pairs_posterior(joint_posterior_df, strip_text = 10, axis_text_size = 7,
                M_j = D_j)
```

#### Marginal posterior distributions

##### Basic reproduction number ($\Re_0$)

```{r}
plot_R0_comparison_by_dataset(posterior_subset, R0_val, 2, 3, D_i, D_j)
```

##### Initial number of infectious individuals ($I_0$)

```{r}
plot_par_estimates_by_dataset(posterior_subset, "I0", 1, x_min = 0,
                              x_max = 3, x_label = "I[0]", D_i, D_j)
```

## Summary

### Coverage


```{r}
actual_values <- data.frame(par = c("R0", "par_rho", "I0"), 
                            actual_val = c(R0_val, rho_val, 1))

map_df(ll_list, calculate_coverage, actual_values, inv_gamma_val) |> 
  pivot_wider(names_from = par, values_from = pct_right) -> coverage_df
```

```{r}
table_coverage(coverage_df)
```